The \dealii{} Library, Version 9.3

### 2021-06-20 9.3/paper.tex
Fix compilation
Change fliped -> reflected

\author[14]{Konrad Simon}
  \affil[14]{Department of Mathematics/Center
  for Earth System Research and Sustainability (CEN), University of
  Hamburg, Grindelberg 5, 20144 Hamburg, Germany.
  \texttt{konrad.simon@uni-hamburg.de}}}

@@

  \item A long standing orientation issue for the vector valued finite
  element \texttt{FE\_RaviartThomas<3>} was resolved. This issue
  prevented the user from using this class on meshes with cells that
  do not have standard orientation, i.e., cells that have faces that
  are flipped and rotated relative to their neighbors. In all eight
  possible neighboring configurations we can now guarantee that the
  necessary $H(\mathrm{div})$-conformity condition is met for all
  polynomaial orders. This is verified through a new conformity test
  on non-standard meshes.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.

>>>>

\author[14]{Konrad Simon}
  \affil[14]{Department of Mathematics/Center
  for Earth System Research and Sustainability (CEN), University of
  Hamburg, Grindelberg 5, 20144 Hamburg, Germany.
  \texttt{konrad.simon@uni-hamburg.de}}

@@

  \item A long standing orientation issue for the vector valued finite
  element \texttt{FE\_RaviartThomas<3>} was resolved. This issue
  prevented the user from using this class on meshes with cells that
  do not have standard orientation, i.e., cells that have faces that
  are reflected and/or rotated relative to their neighbors. In all eight
  possible neighboring configurations, we can now guarantee that the
  necessary $H(\mathrm{div})$-conformity condition is met for all
  polynomaial orders. This is verified through a new conformity test
  on non-standard meshes.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.
